Usage metrics

### 2020-12-16 analysis/usage.Rmd
Calls per run per call sites

>>>>

```{r}
eval_call_triggered %>% 
  filter(average < 50) %>% 
  ggplot(aes(x = average)) +
  geom_histogram(binwidth =  1)

ggsave(path(PLOT_DIR, "calls_per_run_per_call_site.pdf"))

bins <- cut(eval_call_triggered$average, breaks = c(0, 50, 100, 250,500, 1000, 1500,  2000, 3000), include.lowest = TRUE)
sum <- summary(bins)

overview_table(
  r("Runbina", sum[[1]]),
  r("Runbinb", sum[[2]]),
  r("Runbinc", sum[[3]]),
  r("Runbind", sum[[4]]),
  r("Runbine", sum[[5]]),
  r("Runbinf", sum[[6]]),
  r("Runbing", sum[[7]]),
  r("Runbinh", sum[[8]])
)
```
